\section{Conclusion}
\label{sec:conclusion}

MICADO and the ELT will provide the chance to finally resolve the core populations of the densest star clusters in the Milky Way and in many of the galaxies within the local group \textcolor{red}{isn't it 5 Mpc?}.  With MICADO observations of young stellar clusters, one can finally answer the question as to whether the IMF distribution is indeed universal, or whether its shape changes when we leave the solar neighborhood. Currently, these answers are locked inside the dense cores of young stellar clusters, as observations of these clusters are primarily limited by confusion.

The main goal of this work was to determine precisely how much more of these stellar populations will be visible to MICADO. We tried to answer three questions: What is the lowest mass star that MICADO will be able to observe reliably for a given stellar density and distance? What instrumental effects will play a critical role? How many clusters will be available for IMF studies? In order to answer these, we used the instrument simulator for MICADO (SimCADO) to generate synthetic observations of 56 dense stellar regions corresponding to the cores of young stellar clusters at varying distances from Earth. Here we present a summary of the results:

\begin{enumerate}
    \item We have shown that MICADO will easily be able to resolve all members of a stellar population with a density up to 10\h3\,\spa. With proper knowledge of the PSF and an optimized detection and subtraction algorithm densities of 5$\times$10\h3\,\spa should also be achievable.
    
    \item Observations with MICADO will enable direct (resolved) observations of the IMF in well over 1500 young clusters in diverse environments within the local group of galaxies. These observations will provide a statistically meaningful sample for robustly quantifying possible IMF variations and the role of environment on the shape of the IMF.

    % \item Given that MICADO observations will be constrained by the sensitivity to both the brightest and faintest sources in the field of view, MICADO is best suited to investigate the shape of the IMF in clusters in the outer edges of the Milky Way as well as the Magellanic Clouds. For example, MICADO is ideally suited to resolve the IMF in cores of dense young star clusters such as R136 in the LMC and NGC330 in the SMC.
    
    \item MICADO's resolution will allow the peak of the IMF (0.1\,\msun\textless M \textless0.5\,\msune) to be extensively investigated in the Magellanic clouds, and the Salpeter slope of the high mass region of IMF out to distances of 5\,Mpc (M83).
    
    \item Observations focusing on the initial mass function of clusters in the LMC will be limited by sensitivity, not crowding, to 0.1\,\msun. 
    
    \item Investigations of the transition around the hydrogen burning limit (\s0.08\,\msun) will not be possible outside the Milky Way. Instead, brown dwarf populations will be accessible in the cores of the densest Milky Way clusters, e.g. in the Westerlund clusters or the emerging W49A clusters. Objects with masses on the order of 10\,M$_{Jup}$ will be accessible by MICADO for clusters within 8\,kpc of Earth. The only caveat is that an appropriate observation strategy must be found to mask the many bright (m$_{Ks}<15^m$) stars present in all Milky Way clusters.    
    
    \item Finally, accurate knowledge of the ELT's PSF will be absolutely essential for good photometry and PSF subtraction algorithms. The sharp structures created by the segmented mirror design will lead to many fake low luminosity star detections if either the PSF is not well known or the extraction algorithm is not capable of differentiating between a star and an artifact of the PSF.
    
\end{enumerate}


% The parameter space covered distances from 8\,kpc to 5\,Mpc and stellar densities from 10\h2\,\spa to \s10\h5\,\spa - densities much higher then either Hubble or JWST will be capable of resolving. 


% - Answer the questions in the introduction

    % - At distance X and for stellar density Y, down to which mass (Z) can I get an IMF?
    
    % - If variations exist in the IMF, what level could MICADO detect at which distance?
    
% - Brief comparison to JWST's capabilities and where MICADO will accel

% - Brief note on how important the need for PSF-Reconstruction is and how we need to develop tools for source detection and extraction which can properly deal with non-smooth PSFs